\documentclass[11pt,a4paper]{article}
%\pagestyle{headings}
%\linespread{1.6}

% Set up 20 mm margins on each side
\hoffset -5.4mm
\voffset -5.4mm

\oddsidemargin 0.0in
\evensidemargin 0.0in

\textwidth 17.0cm
\textheight 232mm

\topmargin 0.0in
\headheight 4mm
\headsep 9mm
\footskip 12mm

%\usepackage{hyperref,color,graphicx,braket,mathrsfs,simplewick,slashed,amsmath,amssymb,feynmf,ifpdf,pdflscape,wrapfig,fancyhdr,lastpage,etoolbox}
\usepackage{hyperref,xcolor,graphicx,ifpdf,wrapfig,fancyhdr,lastpage,etoolbox,tocloft,multirow,array,pdflscape,enumitem,eurosym,amssymb,titlesec,multirow,footnote,color,colortbl,scrextend,etoolbox}
\usepackage[square,numbers]{natbib}
%\usepackage[backend=bibtex,style=authoryear]{biblatex}
%\addbibresource{/home/josh/Dropbox/bibliography/xenon_fulbright.bib}

\hypersetup{colorlinks,%
            citecolor=black,%
            linkcolor=black,%
            filecolor=black,%
            urlcolor=black}
        
%\makesavenoteenv{tabular}
\definecolor{Gray}{gray}{0.95}

\bibliographystyle{JHEP}
%\bibliographystyle{apsrev4-1}

% Set up the header and footer.
\makeatletter
\patchcmd{\@fancyhead}{\rlap}{\color{black}\rlap}{}{}
\patchcmd{\@fancyfoot}{\rlap}{\color{black}\rlap}{}{}
\makeatother

% Set up the title spacing
\titlespacing\section{0pt}{4pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{4pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{4pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\lhead{Renner}
\chead{Part B1}
\rhead{DNNEXT}
\cfoot{\thepage}

% To keep the numbering of the table of contents consistent.
\tocloftpagestyle{fancy}

% Table column formatting: from 
% http://tex.stackexchange.com/questions/12703/how-to-create-fixed-width-table-columns-with-text-raggedright-centered-raggedlef
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\begin{document}
\input{Commands.tex}

\begin{center}
\large
\textbf{ERC Starting Grant 2017}\\
Research proposal [Part B1]\\[2.0\baselineskip]
\Large
\textbf{Deep Learning in Detector Physics Analyses}\\[1.0\baselineskip]
\LARGE
\textbf{DNNEXT}\\[1.0\baselineskip]
\end{center}
% \vspace{5.5 in}

\noindent PI: Joshua Edward Renner\\
\noindent Host Institution: Universidad de Valencia\\
\noindent Proposal Duration: 60 months\\

The development of deep learning has been realized over the past 10 years with the rise of computing power, which has now permitted the training of neural networks with many layers
of neurons in series.  Such networks have proven capable of high-level abstraction, that is, neurons in deeper layers have been shown to indicate the presence of complex features in a dataset, 
such as the presence of macroscopic objects in images.  It is of great interest to study how such techniques can be applied to physics, and in particular particle detection and tracking, a field 
in which problems exist similar to those to which deep learning has been initially applied.  We propose an in-depth study of the use of deep neural networks in the reconstruction and classification of events in NEXT (Neutrino Experiment with a Xenon TPC), an experiment searching for neutrinoless double beta decay in $^{136}$Xe. We discuss the results that have already been obtained which indicate the advantages of deep neural networks over classical analysis methods and highlight their merit for further study.
\newpage
\normalsize

\newpage
%\setcounter{page}{1}
{\textbf{Section A: Extended Synopsis of the scientific proposal}}

\newpage
\noindent{\textbf{Section B: Curriculum Vitae}}\\[1.0\baselineskip]
\input{src/renner_CV.tex}

\newpage
{\textbf{\emph{Appendix: All on-going and submitted grants and funding of the PI (Funding ID)}}}\\

\noindent\textbf{On-going grants}\\

\noindent\textbf{Grant applications}\\

\newpage
{\textbf{Section C: Early achievements track-record}}\\

\noindent \textbf{PUBLICATIONS AS LEAD AUTHOR AND/OR PRINCIPAL CONTRIBUTOR}\\

\noindent J. Renner \emph{et al.} (NEXT Collaboration).  Background rejection in NEXT using deep neural networks.  arXiv:1609.06202 (2016)\\

\noindent J. Renner, A. Cervera, J. A. Hernando, A. Imzaylov, F. Monrabal, J. Mu\~noz, D. Nygren, and J.J. Gomez-Cadenas.  Improved background rejection in neutrinoless double beta decay experiments using a magnetic field in a high pressure xenon TPC.  JINST 10 (2015) P12020. (arXiv:1509.01821)\\

\noindent J. Renner \emph{et al.} (NEXT Collaboration).  Ionization and scintillation of nuclear recoils in gaseous xenon.  Nucl. Instr. Meth. A 793, 62 (2015).  (arXiv:1409.2853)\\

\noindent V.\ \'{A}lvarez \emph{et al.} (NEXT Collaboration). Near-intrinsic energy resolution for 30 to 662 keV gamma rays in a high pressure xenon electroluminescent TPC. Nucl. Instr. Meth. A 708, 
101 (2013).\\(arXiv:1211.4474)\\
% available online January 18, 2013

\noindent \textbf{SELECTED CONFERENCE PRESENTATIONS}\\

\noindent J. Renner, V. M. Gehman, A. Goldschmidt, D. Nygren, and C.A.B. Oliveira, for the NEXT Collaboration. 
Characterization of Nuclear Recoils in High Pressure Xenon Gas: Towards a Simultaneous Search for WIMP Dark Matter and Neutrinoless 
Double Beta Decay.  TAUP 2013 (presentation by J. Renner on Sept. 11, 2013). Phys. Procedia 61, 766 (2015).\\

\noindent Nuclear Recoils and Recombination in High Pressure Xenon Gas.  Advances in Neutrino Technologies (ANT) 2013 
(presentation by J. Renner on May 11, 2013).\\

\noindent A. Goldschmidt, T. Miller, D. Nygren, J. Renner, D. Shuman, H. Spieler, and J. White.
High-pressure xenon gas TPC for neutrino-less double-beta decay in 136Xe: Progress toward the goal of 1\% FWHM energy resolution.” 
2011 IEEE Nuclear Science Symposium (presentation by J. Renner on Oct. 26, 2011).\\

\newpage
\bibliography{dnnext}

\end{document}