\vspace{0.5cm}
{\noindent\textbf{Current professional address}}

\begin{tabular*}{\textwidth}{lcr}
Instituto de F\'isica Corpuscular & \hspace{1.2in} & Phone: +34 963543713\\
C/ Catedr\'atico Jos\'e Beltr\'an, 2 & & Mobile Phone: +34 603659293\\
Paterna, Valencia 46980 (Espa\~na) & & Email: jrenner@ific.uv.es\\
&&\\
\end{tabular*}

{\noindent\textbf{Research interests}}\\

\indent\hspace{0.2 cm}\textbullet\,\,Design, analysis, and simulation of particle detectors\\
\indent\hspace{0.2 cm}\textbullet\,\,Neutrinoless double-beta decay\\
\indent\hspace{0.2 cm}\textbullet\,\,Deep learning\\

{\noindent\textbf{Education}}\\

\indent\hspace{0.2 cm}UNIVERSITY OF CALIFORNIA, Berkeley, CA (U.S.A.)\\ 
\indent\hspace{0.2 cm}Aug 2009 - May 2014\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\,Ph.D. in Physics, May 2014\\ % (GPA = 3.968/4.0; 4.0 = A)\\
\indent\hspace{0.2 cm}\hspace{1.2 cm}-\,\,Advisor: Prof.\ James Siegrist\\
\indent\hspace{0.2 cm}\hspace{1.2 cm}-\,\,Thesis: High Pressure Xenon Detectors for Rare Physics Searches\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\,Master of Arts in Physics, May 2011\\

\indent\hspace{0.2 cm}GEORGIA INSTITUTE OF TECHNOLOGY, Atlanta, GA (U.S.A.)\\
\indent\hspace{0.2 cm}Aug 2005 - May 2009\\

\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\,Bachelor of Science in Physics, May 2009\\ %(GPA = 4.0/4.0; 4.0 = A)\\

{\noindent\textbf{Research and teaching experience}}\\

\indent\hspace{0.2 cm}FULBRIGHT POSTDOCTORAL RESEARCHER\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\emph{at Instituto de F\'{i}sica Corpuscular (IFIC)}\hspace{3.9 cm}Sept 15, 2015 - June 15, 2016\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\hspace{0.6 cm}\textbullet\,\, Continued work on NEXT experiment\\

\indent\hspace{0.2 cm}INSTITUTO DE F\'{I}SICA CORPUSCULAR (IFIC)\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\emph{Investigador Doctor Junior} (Postdoctoral Research)\hspace{3.1 cm}Oct 2014 - July 2015\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\hspace{0.6 cm}\textbullet\,\, Conducted simulation-based studies and developed\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\hspace{0.6 cm}\,\,\,\,\,\,\,algorithms for topological characterization of electron\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\hspace{0.6 cm}\,\,\,\,\,\,\,tracks in high pressure xenon detectors\\

\indent\hspace{0.2 cm}LAWRENCE BERKELEY NATIONAL LABORATORY (LBNL)\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\emph{Affiliate (Independent Scholar)}\hspace{6.6 cm}May 2014 - Sep 2014\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\hspace{0.6 cm}\textbullet\,\, Continuation of work from graduate studies\\

\newpage

\indent\hspace{0.2 cm}LAWRENCE BERKELEY NATIONAL LABORATORY (LBNL)\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\emph{Graduate Student Research}\hspace{7.1 cm}May 2009 - May 2014\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\hspace{0.6 cm}\textbullet\,\, Operated and serviced high pressure xenon detector\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\hspace{0.6 cm}\textbullet\,\, Designed and implemented data analysis and acquisition software\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\hspace{0.6 cm}\textbullet\,\, Characterized response of high pressure xenon gas to electronic\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\hspace{0.6 cm}\,\,\,\,\,\,\,and nuclear recoils\\

\indent\hspace{0.2 cm}LAWRENCE LIVERMORE NATIONAL LABORATORY (LLNL)\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\emph{Graduate Student Research}\hspace{7.1 cm}May 2010 - Aug 2010\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\hspace{0.6 cm}\textbullet\,\, Developed simulations for gas-based particle detectors\\
%\indent\hspace{0.2 cm}\hspace{0.6 cm}\hspace{0.6 cm}\textbullet\,\, Worked geared toward Negative Ion TPC detector\\

\indent\hspace{0.2 cm}UNIVERSITY OF CALIFORNIA, BERKELEY\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\emph{Graduate Student Instructor}\hspace{6.9 cm}Aug 2009 - Dec 2009\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\hspace{0.6 cm}\textbullet\,\, Course: Physics 111, Basic Semiconductor Circuits Laboratory\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\hspace{0.6 cm}\textbullet\,\, Assisted in laboratory activities and graded laboratory assignments\\

\indent\hspace{0.2 cm}GEORGIA TECH RESEARCH INSTITUTE (GTRI)\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\emph{Student Employee}\hspace{4.8 cm}May 2007 - Aug 2007, Jan 2008 - Aug 2008\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\hspace{0.6 cm}\textbullet\,\, Worked as student engineer in the Radar Warning Receiver division\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\hspace{0.6 cm}\textbullet\,\, Simulated and tested a CPU design using programmable digital logic\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\hspace{0.6 cm}\textbullet\,\, Improved an existing radar direction-finding algorithm\\

\noindent \textbf{Publications as the lead author and/or a principal contributor}\\

\noindent J. Renner, A. Cervera, J. A. Hernando, A. Imzaylov, F. Monrabal, J. Mu\~noz, D. Nygren, and J.J. Gomez-Cadenas.  Improved background rejection in neutrinoless double beta decay experiments using a magnetic field in a high pressure xenon TPC.  arXiv:1509.01821 [physics.ins-det].\\

\noindent J. Renner \emph{et al.} (NEXT Collaboration).  Ionization and scintillation of nuclear recoils in gaseous xenon.  Nucl. Instr. Meth. A 793, 62 (2015).  (arXiv:1409.2853 [physics.ins-det])\\

\noindent V.\ \'{A}lvarez \emph{et al.} (NEXT Collaboration). Near-intrinsic energy resolution for 30 to 662 keV gamma rays in a high pressure xenon electroluminescent TPC. Nucl. Instr. Meth. A 708, 
101 (2013).\\(arXiv:1211.4474 [physics.ins-det])\\
% available online January 18, 2013

\noindent \textbf{Publications as co-author}\\

\noindent C.\ Cebri\'an \emph{et al.} (NEXT Collaboration). Radiopurity assessment of the tracking readout for the NEXT double beta decay experiment.
JINST 10, P05006 (2015).  (arXiv:1411:1433 [physics.ins-det])\\
% published May 13, 2015 

\noindent L.\ Serra \emph{et al.} (NEXT Collaboration). An improved measurement of electron-ion recombination in high-pressure xenon gas.
JINST 10, P03025 (2015).  (arXiv:1412.3573 [physics.ins-det])\\
% published March 26, 2015

\noindent D.\ Lorca \emph{et al.} (NEXT Collaboration). Characterization of NEXT-DEMO using xenon $K_{\alpha}$ x-rays.
JINST 9, P10007 (2014).  (arXiv:1407.3966 [physics.ins-det])\\
% published October 13, 2014

\newpage
\noindent J.\ J.\ G\'{o}mez-Cadenas \emph{et al.} (NEXT Collaboration). Present Status and Future Perspectives of the NEXT Experiment.  Advances in High Energy Physics 2014, 907067
(2014).\\(arXiv:1307.3914 [physics.ins-det])\\

\noindent V.\ \'{A}lvarez \emph{et al.} (NEXT Collaboration). Description and commissioning of NEXT-MM prototype: first results from operation in a Xenon-Trimethylamine gas mixture.
JINST 9, P03010 (2014).\\(arXiv:1311.3242 [physics.ins-det])\\
% published March 18, 2014

\noindent V.\ \'{A}lvarez \emph{et al.} (NEXT Collaboration). Operation and first results of the NEXT-DEMO prototype using a silicon photomultiplier tracking array.
JINST 8, P09011 (2013).\\(arXiv:1306.0471 [physics.ins-det])\\
% published September 20, 2013

\noindent V.\ \'{A}lvarez \emph{et al.} (NEXT Collaboration). Ionization and scintillation response of high-pressure xenon gas to alpha particles.
JINST 8, P05025 (2013). (arXiv:1211.4508 [physics.ins-det])\\
% published May 31, 2013

\noindent V.\ \'{A}lvarez \emph{et al.} (NEXT Collaboration). Design and characterization of the SiPM tracking system of NEXT-DEMO, a demonstrator prototype of the NEXT-100 experiment.
JINST 8, T05002 (2013).\\(arXiv:1206.6199 [physics.ins-det])\\
% published May 15, 2013

\noindent V.\ \'{A}lvarez \emph{et al.} (NEXT Collaboration). Initial results of NEXT-DEMO, a large-scale prototype of the NEXT-100 experiment.
JINST 8, P04002 (2013). (arXiv:1211.4838 [physics.ins-det])\\
% published April 3, 2013

\noindent V.\ \'{A}lvarez \emph{et al.} (NEXT Collaboration). Radiopurity control in the NEXT-100 double beta decay experiment: procedures and initial measurements.
JINST 8, T01002 (2013).\\(arXiv:1211.3961 [physics.ins-det])\\
% published January 22, 2013

\noindent V.\ \'{A}lvarez \emph{et al.} (NEXT Collaboration). NEXT-100 Technical Design Report (TDR). Executive summary.
JINST 7 T06001 (2012). (arXiv:1202.0721 [physics.ins-det])\\
% published June 6, 2012

\noindent P. Sorensen, M. Heffner, A. Bernstein, J. Renner, and M. Sweany. Towards energy resolution at the statistical limit from a negative ion time projection 
chamber. Nucl. Instr. Meth. A. 686, 106 (2012). (arXiv:1205.6427v1 [physics.ins-det])\\
% available online June 2, 2012

\noindent V.\ \'{A}lvarez \emph{et al.} (NEXT Collaboration). SiPMs coated with TPB: coating protocol and characterization for NEXT.
JINST 7, P02010 (2012). (arXiv:1201.2018 [physics.ins-det])\\
% published Feb. 22, 2012

\noindent \textbf{Selected conference presentations}\\

\noindent J. Renner, V. M. Gehman, A. Goldschmidt, D. Nygren, and C.A.B. Oliveira, for the NEXT Collaboration. 
Characterization of Nuclear Recoils in High Pressure Xenon Gas: Towards a Simultaneous Search for WIMP Dark Matter and Neutrinoless 
Double Beta Decay.  TAUP 2013 (presentation by J. Renner on Sept. 11, 2013). Phys. Procedia 61, 766 (2015).\\

\noindent Nuclear Recoils and Recombination in High Pressure Xenon Gas.  Advances in Neutrino Technologies (ANT) 2013 
(presentation by J. Renner on May 11, 2013).\\

\newpage
\noindent A. Goldschmidt, T. Miller, D. Nygren, J. Renner, D. Shuman, H. Spieler, and J. White.
High-pressure xenon gas TPC for neutrino-less double-beta decay in 136Xe: Progress toward the goal of 1\% FWHM energy resolution.” 
2011 IEEE Nuclear Science Symposium (presentation by J. Renner on Oct. 26, 2011).\\

{\noindent\textbf{Summary of key research contributions to the NEXT Collaboration}}\\

\indent\hspace{0.2 cm}\textbullet\,\,Assisted in construction and operation of LBNL prototype detector\\
\indent\hspace{0.2 cm}\,\,\,\,\,\,\,- Primary author of automated data readout and analysis code\\
\indent\hspace{0.2 cm}\,\,\,\,\,\,\,- Worked on detector electronics and gas system, and PMT calibration\\
\indent\hspace{0.2 cm}\textbullet\,\,Assisted in mentoring undergraduate students working in the LBNL group\\
\indent\hspace{0.2 cm}\textbullet\,\,Played a key role in demonstrating 1\% FWHM energy resolution at 662 keV for electrons\\
\indent\hspace{0.2 cm}\,\,\,\,\,\,\,\,in high pressure xenon gas\\
\indent\hspace{0.2 cm}\textbullet\,\,Assisted in development of detector Monte Carlo and its execution in supercomputing\\
\indent\hspace{0.2 cm}\,\,\,\,\,\,\,\,environment\\
\indent\hspace{0.2 cm}\textbullet\,\,Measured ionization and scintillation produced by nuclear recoils in high pressure xenon\\
\indent\hspace{0.2 cm}\,\,\,\,\,\,\,\,gas\\
\indent\hspace{0.2 cm}\textbullet\,\,Developed algorithms to improve background rejection based on event topology\\

{\noindent\textbf{Contributions to open-source projects}}\\

\indent\hspace{0.2 cm}Detector Simulation in Garfield++ with Open-Source Finite Element Electrostatics\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\, Detector simulation methodology, contributed code and documentation\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\, See: http://garfieldpp.web.cern.ch/garfieldpp/examples/elmer\\

{\noindent\textbf{Workshops and specialized schools attended}}\\

\indent\hspace{0.2 cm}TAUP 2013 Summer School on Astroparticle and Underground Science\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\, Lecture series\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\, Asilomar Conference Grounds, Asilomar, CA (U.S.A.)\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\, Sept. 4-8, 2013\\

\indent\hspace{0.2 cm}Excellence in Detectors and Instrumentation Technologies (EDIT) Symposium\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\, Series of lectures and laboratory courses\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\, Fermi National Accelerator Laboratory, Batavia, IL (U.S.A.)\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\, Feb. 13-24, 2012\\

{\noindent\textbf{Awards and honors}}\\

\indent\hspace{0.2 cm}Fulbright Postdoctoral Researcher Grant (September 15, 2015 - June 14, 2016)\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\,9-month research award to continue work on NEXT\\

\indent\hspace{0.2 cm}Department of Energy National Nuclear Security Administration\\
\indent\hspace{0.2 cm}Stewardship Science Graduate Fellowship (2009-2013)\\
%\indent\hspace{0.2 cm}\hspace{1.25 cm}\textbullet\,\, Sept 2009 - Aug 2013\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\,4-year fellowship covering tuition and fees plus monthly stipend for graduate study\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\,\,\,\,\,\,\,at a U.S. university\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\,See: \href{http://www.krellinst.org/ssgf}{http://www.krellinst.org/ssgf}\\

\indent\hspace{0.2 cm}The Hitohiro Fukuyo Memorial Scholarship (2009)\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\, Achievement award granted by the Physics department at Georgia Tech\\

\indent\hspace{0.2 cm}Henry Ford II Scholar Award (2008)\\ % April 15, 2008
\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\, Awarded for outstanding achievement in engineering at Georgia Tech\\

\indent\hspace{0.2 cm}Georgia HOPE Scholarship (2005-2009)\\ % Fall 2005 - Spring 2009
\indent\hspace{0.2 cm}\hspace{0.6 cm}\textbullet\,\, Scholarship granted to in-state students maintaining a GPA of at least 3.0 at a public\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\,\,\,\,\,\,\,university in the state of Georgia; covered tuition, some mandatory fees, and provided\\
\indent\hspace{0.2 cm}\hspace{0.6 cm}\,\,\,\,\,\,\,a book allowance\\

%{\noindent\textbf{Skills and personal development}}\\
%
%\indent\hspace{0.2 cm}\textbullet\,\,Languages: English (native), French (good), and Spanish (good)\\
%
%\indent\hspace{0.2 cm}\textbullet\,\,Strong knowledge of software tools used in a research environment:\\
%\indent\hspace{0.5 cm}- Extensive programming experience; knowledge of C++, Java, ROOT, Python\\
%\indent\hspace{0.5 cm}- Experienced working in a Linux environment\\